Benchmarking figures

### 2016-05-17 results/figures.Rmd
clean up

```{r,duplicates,fig.height=5,fig.width=3.4}
dup.df<-read.csv("../data/process/2015-11-14/Variants/all.sum.csv",stringsAsFactors = F,comment.char = "#")
#sum.df<-read.csv("~/Box Sync/Lab_work/NGS/Benchmarking/data/2015-11-14/all.sum.csv")
pat<-"([0-9]+)_([0-9]+)_([0-9]+)"
mutate(dup.df, exp.freq = sub(pat,"\\2",Id),
       dup = as.numeric(sub(pat,"\\3",Id)),
)-> dup.df

@@

dup.df<-mutate(dup.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
dup.df$category[dup.df$mutation %in% wt_mut]<-"wt"
dup.df$category[dup.df$mutation %in% mfe.df$mutation]<-"mfe"

cut.df<-subset(dup.df,Phred>35 & MapQ>30 & Read_pos<94 & Read_pos>32)

>>>>

```{r,duplicates,fig.height=5,fig.width=3.4}
dup.df<-read.csv("../data/process/2015-11-14/Variants/all.sum.csv",stringsAsFactors = F,comment.char = "#")
pat<-"([0-9]+)_([0-9]+)_([0-9]+)"
mutate(dup.df, exp.freq = sub(pat,"\\2",Id),
       dup = as.numeric(sub(pat,"\\3",Id))
)-> dup.df

@@

dup.df<-mutate(dup.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
#dup.df$category[dup.df$mutation %in% wt_mut]<-"wt" There are no wt mutants see wt_mut. For some reason this was causing an error.
dup.df$category[dup.df$mutation %in% mfe.df$mutation]<-"mfe"

cut.df<-subset(dup.df,Phred>=35 & MapQ>=30 & Read_pos<=94 & Read_pos>=32)
